Guarded Recursion in Agda via Sized Types

### 2019-01-15 code-oneclock-paper/latex/paper.tex
acks, funding, orcid

\author{Niccol\`o Veltri}{Department of Computer Science, IT
  University of Copenhagen, Denmark}{nive@itu.dk}{[orcid]}{[funding]}

@@

\acknowledgements{Acknowledge Andrea Vezzosi.}%optional

@@

\subsection{The Later Modality}
\input{CloTT/TypeFormers/Later}
\input{CloTT/TypeFormers/Fix}
\input{CloTT/TypeFormers/Force}

>>>>

\author{Niccol\`o Veltri}{Department of Computer Science, IT
  University of Copenhagen, Denmark}{nive@itu.dk}{https://orcid.org/0000-0002-7230-3436}{This work was supported by a research grant (13156) from VILLUM FONDEN,
  and by DFF-Research Project 1 Grant no. 4002-00442, from The Danish Council 
  for Independent Research for the Natural Sciences (FNU).}

@@

\acknowledgements{We are thankful to Andreas Abel, Herman Geuvers,
  Rasmus Ejlers M{\o}gelberg and Andrea Vezzosi for discussions and
valuable hints.}%optional

@@

\subsection{The Later Modality}
\label{sec:later}
\input{CloTT/TypeFormers/Later}
\input{CloTT/TypeFormers/Fix}
\input{CloTT/TypeFormers/Force}
